Demography and linked selection in wild and domesticated maize

### 2015-08-15 manuscript.tex
done with results

\subsection{Population expansion leads to stronger purifying selection in modern maize}
Motivated by the rapid post-domestication expansion of maize evident from our demographic analysis, we investigated whether patterns of diversity at low frequency --- and thus on average younger --- polymorphisms would show similar results in comparisons of maize and teosinte.
We thus repeated our analysis of diversity using alleles present in only a single individual in the sample.
In direct contrast to patterns observed for pairwise nucleotide diversity (Figure \ref{fig:purify}A), diversity of singletons was more strongly reduced in and near genes in maize than in teosinte (Figure \ref{fig:purify}B).  
This pattern remained after downsampling our maize data to account for differences in sample size. 
Taken together, these results suggest that demographic history and population size change have impacted the efficacy of purifying selection during maize evolution.

Patterns of diversity around substitutions, however

>>>>

\subsection{Population expansion leads to stronger purifying selection in modern maize}
Motivated by the rapid post-domestication expansion of maize evident from our demographic analysis, we investigated whether patterns of diversity at low frequency --- and thus on average younger --- polymorphisms would show similar results in comparisons of maize and teosinte.
We thus repeated our analysis of diversity using alleles present in only a single individual in the sample.
In direct contrast to patterns observed for pairwise nucleotide diversity (Figure \ref{fig:purify}A), diversity of singletons was more strongly reduced in and near genes in maize than in teosinte (Figure \ref{fig:purify}B).  
This pattern remained after downsampling our maize data to account for differences in sample size. \jri{we should test singleton curve for genes not in 20\% highest H12 also!}

These results suggest that demographic history and population size change have impacted the efficacy of purifying selection during maize evolution.
In contrast, analysis of singleton diversity around missense and synonymous substitutions (Figure \ref{sFig:singleton}) provides a nearly identical pattern to that shown in Figure \ref{fig:hardSweeps}, providing little support for a substantial increase in the number or strength of hard sweeps occurring in maize.
